Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex

From the results we can see that only the first variable (i.e. the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence. The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis by using the first difference tweet count, which fulfills the stationarity requirement.\\

Secondly, we have to check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price). Here we also included the first difference (variable name: df\_bpi\_closing\_price) and the logarithmic first difference (variable name: log\_df\_bpi\_closing\_price) transformations. The ADF test for these variables gives the following results:\\

@@

These result also suggest to use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.

>>>>

From the results we can see that only the first variable (i.e. the untransformed tweet count) is non-stationary, since the absolute value of the Test Statistic (3.152) is smaller than the absolute value of the 1\% critical value (3.475), the null hypothesis of non-stationarity cannot be rejected as a consequence. The second variable is stationary (14.167 $>$ 3.475) and from here onwards we shall proceed the analysis with only the first difference tweet count, whose test statistic falls furthest into the rejection zone.\\

Out of the similar concern stated above, we shall check for stationarity for the second variable, the bitcoin prices (variable name: bpi\_closing\_price). As before, we also include the first difference bitcoin prices (variable name: df\_bpi\_closing\_price) and the logarithmic first difference ones (variable name: log\_df\_bpi\_closing\_price) transformations. The ADF test for these variables gives the following results:\\

@@

Once again, the test result suggests we use the first difference transformation of the variable bitcoin prices, for stationarity to be fulfilled.
